---
title: "R5"
author: "Hoste Aliona"
date: "03/11/2020"
output: html_document
---

### Exercice 1
###### For the data InsectSpray, make a table for the number of insects for each spray with the mean, median and standard error.
###### Note: Remember to use knitr::kable(), or a similar function to print the table with its caption.

```{r exercice 1, include=TRUE}
InsectSprays <- InsectSprays

Spray <- factor()
Count <- integer()
SS <- integer()
Mean <- integer()
Median <- integer()
Standard_error <- integer()

# create Spray vectors with all the levels 
for(i in levels(InsectSprays$spray)){
  Spray <- c(Spray,i)
}
# or Spray <- levels(InsectSprays$spray)

# create the Count vector where i takes each value of Spray (A, B, C...) and do the sum of count for each Spray categories
for(i in Spray){
  SS <- subset(InsectSprays$count,InsectSprays$spray == i)
  Count <- c(Count, sum(SS))
  Mean <- c(Mean, mean(SS))
  Median <- c(Median, median(SS))
  Standard_error <- c(Standard_error, sd(SS)/sqrt(length(SS)))
}

# Create the data frame
Datatable <- data.frame(Spray, Count, Mean, Median, Standard_error)


knitr::kable(Datatable, caption = "Table for the number of insects for each spray with the mean, median and standard error")

```




### Exercice 2
######Print a plot to see the differences of counts between sprays. Include a caption explaining the figure. 
###### Which type of plot is the one you choose and why? barplot because we have a continuous variable in function of categories
```{r exercice 2, fig.cap=cap,echo=TRUE}
barplot(Datatable$Count ~ Datatable$Spray, Datatable, col= as.factor(Datatable$Spray), ylab = "Count", xlab = "Spray") 
cap <- character()
cap <- "Figure 1: Differences of counts between sprays "
legend("top", legend = paste("Spray =", Spray), lty = 1, col = 1:6)

```


### Exercice 3
###### Test for differences between sprays using anova and a posthoc comparison and redo the previous plot including the representation of all posthoc differences.
###### Note: for the anova use the command aov() and for the posthoc comparison use the Tukey’s ‘Honest Significant Difference’ method. For this method try the TukeyHSD() and the agricolae::HSD.test() and see the differences.
```{r exercice 3, echo=TRUE}
# Create object with anova
a1 <- aov(count ~ spray, data = InsectSprays)

#Visualise results for anova test
anova(a1)

#Plot anova
plot(a1)

TukeyHSD(a1)

#install.packages("agricolae")
library("agricolae")
a3 <- agricolae::HSD.test(a1, "spray")
a3


```

######We can see that using **agricolae::HSD.test** is easier to get informations


### Exercice 4
```{r exercice 4, echo=TRUE}


```

### Exercice 5
```{r exercice 5, fig.cap=cap,echo=TRUE}


```


### Exercice 6
```{r exercice 6, fig.cap=cap,echo=TRUE}


```


### Exercice 7
```{r exercice 7, fig.cap=cap,echo=TRUE}


```